---
title: "ADSProj1"
author: "Wenwen Shen"
date: "9/15/2019"
output: html_document
---

```{r load libraries, warning=FALSE, message=FALSE,echo=FALSE}
library(tidyverse)
library(tidytext)
library(plotly)
library(DT)
library(tm)
library(data.table)
library(scales)
library(wordcloud)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny) 
library(ggplot2)
```
#Part1: Load data
###I loaded data of artist and processed lyrics. And I also creadted a emotional vector, which contains "love", "happy", "joy", "smile", "sweet","sad", "anger", "fear","cry","hate","fear". To check if the emotional is different from each period and each genre. 
```{r load data, warning=FALSE, message=FALSE, echo=FALSE}
# load lyrics data
load('/Users/wenwen/Downloads/github/Github/fall2019-proj1--Minaririri/output/processed_lyrics.RData')
#load('../output/processed_lyrics.RData') 
# load artist information
dt_artist <- fread('/Users/wenwen/Downloads/github/Github/fall2019-proj1--Minaririri/data/artists.csv')
#dt_artist <- fread('../data/artists.csv') 

time_list <- c("1970s", "1980s", "1990s", "2000s", "2010s")
lyrics_list <- c("Folk", "R&B", "Electronic", "Jazz", "Indie", "Country", "Rock", "Metal", "Pop", "Hip-Hop", "Other")
emo.vector <- c("love","happy","joy","smile","sweet","sad", "anger", "fear","cry","hate","fear")
head(dt_lyrics,10)
```

#Part2: Frequency of emotional words by years. 
###I checked the frequency words for each time periods, but the frequency of each emotional word are not very different during 1970s to 2010s. 
```{r, echo=FALSE}
#Filtered dt_lyrics by years. 
temp.1970s <- dt_lyrics %>% filter(year >= 1970) %>% filter(year < 1980)
freq.1970s <- strsplit(temp.1970s$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)

temp.1980s <- dt_lyrics %>% filter(year >= 1980) %>% filter(year < 1990)
freq.1980s <- strsplit(temp.1980s$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)

temp.1990s <- dt_lyrics %>% filter(year >= 1990) %>% filter(year < 2000)
freq.1990s <- strsplit(temp.1990s$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)

temp.2000s <- dt_lyrics %>% filter(year >= 2000) %>% filter(year < 2010)
freq.2000s <- strsplit(temp.2000s$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)

temp.2010s <- dt_lyrics %>% filter(year >= 2010) %>% filter(year < 2020)
freq.2010s <- strsplit(temp.2010s$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)

data.emotionalwords.year <- data.frame(Word=freq.1970s$., Freq1970s=freq.1970s$Freq/nrow(temp.1970s),Freq1980s=freq.1980s$Freq/nrow(temp.1980s), Freq1990s=freq.1990s$Freq/nrow(temp.1990s),Freq2000s=freq.2000s$Freq/nrow(temp.2000s), Freq2010s=freq.2010s$Freq/nrow(temp.2010s))
data.emotionalwords.year
```
```{r, echo=FALSE}
par(mfrow=c(2,3))
barplot(data.emotionalwords.year$Freq1970s, horiz = T, axes = T, names.arg = "1970s")
barplot(data.emotionalwords.year$Freq1980s, horiz = T, axes = T, names.arg = "1980s")
barplot(data.emotionalwords.year$Freq1990s, horiz = T, axes = T, names.arg = "1990s")
barplot(data.emotionalwords.year$Freq2000s, horiz = T, axes = T, names.arg = "2000s")
barplot(data.emotionalwords.year$Freq2010s, horiz = T, axes = T, names.arg = "2010s")
```



#####Conclution from part2: from the picture above, we could find that no matter which years, the freqency of using emotional words doesn't change too much. 

#Part3: Frequency of emotional words by genre. 
###I am trying to find which kind of emotion is stronger, seperated by different genre. 

##3.1  Filtered lyrics by genre.
###I filtered the words by emotional words from genre and emo.vector. Then, I calculated the frequency of each word by dividing the number of the songs from that genre. After that, I used frequency of each word from each genre to form a data frame. 
```{r, echo=FALSE}
temp.folk <- dt_lyrics %>% filter(genre=="Hip-Hop")
freq.folk <- strsplit(temp.folk$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)
freq.folk<-cbind(freq.folk, freq.folk$Freq/nrow(temp.folk))

temp.metal <- dt_lyrics %>% filter(genre=="Metal")
freq.metal <- strsplit(temp.metal$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)
freq.metal<-cbind(freq.metal, freq.metal$Freq/nrow(temp.metal))

temp.elec <- dt_lyrics %>% filter(genre=="Electronic")
freq.elec <- strsplit(temp.elec$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)
freq.elec<-cbind(freq.elec, freq.elec$Freq/nrow(temp.elec))

temp.coun <- dt_lyrics %>% filter(genre=="Country")
freq.coun <- strsplit(temp.coun$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)
freq.coun<-cbind(freq.coun, freq.coun$Freq/nrow(temp.coun))

temp.RB <- dt_lyrics %>% filter(genre=="R&B")
freq.RB <- strsplit(temp.RB$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)
freq.RB<-cbind(freq.RB, freq.RB$Freq/nrow(temp.RB))

temp.HH <- dt_lyrics %>% filter(genre=="Hip-Hop")
freq.HH <- strsplit(temp.HH$stemmedwords, " ") %>% unlist() %>% table() %>% as.data.frame()  %>% filter(. %in% emo.vector)
freq.HH<-cbind(freq.HH, freq.HH$Freq/nrow(temp.HH))
```

```{r,echo=FALSE}
data.gen <- data.frame(freq.folk$., freq.folk$`freq.folk$Freq/nrow(temp.folk)`,
                       freq.coun$`freq.coun$Freq/nrow(temp.coun)`,
                       freq.elec$`freq.elec$Freq/nrow(temp.elec)`,
                       freq.metal$`freq.metal$Freq/nrow(temp.metal)`,
                       freq.RB$`freq.RB$Freq/nrow(temp.RB)`, 
                       freq.HH$`freq.HH$Freq/nrow(temp.HH)`)
names(data.gen) <-c("Words", "Folk", "Country", "Electronic", "Metal", "R&B","Hip-Hop")
data.gen
```


## 3.2: Comparison of Metal and Country
###From the table above, I decided to choose Metal and Country to compare. For the picture below, the left ones are Metal, and the right ones are Country. 
```{r,echo=FALSE}
par(mfrow=c(1,2))
wordcloud(freq.metal$., freq.metal$Freq, colors=brewer.pal(8, "Accent"))
wordcloud(freq.coun$., freq.coun$Freq, colors=brewer.pal(8, "Accent"))
```


#####From the size of each emotional words above, we could easily find Metal is more emotional, since the "fear" and "hate" shows a lot. However, Country is more gentle. There are more clear comparison below. 

####Frequency of emotional words from Metal and Country. 
```{r, echo=FALSE}
df.m <- data.frame(Word = freq.metal$., Freq=freq.metal$`freq.metal$Freq/nrow(temp.metal)` )
ggplot(df.m, aes(y=df.m$Freq, x=reorder(df.m$Word, df.m$Freq))) +geom_bar(stat = "identity")+coord_flip()+xlab("emotional words from Metal") + ylab("frequency")
```
```{r, echo=FALSE}
df.c <- data.frame(Word=freq.coun$., Freq=freq.coun$`freq.coun$Freq/nrow(temp.coun)`)
ggplot(df.c, aes(y=df.c$Freq, x=reorder(df.c$Word, df.c$Freq))) +geom_bar(stat = "identity")+coord_flip()+xlab("emotional words from Country") + ylab("frequency")
```


##3.3 Wordcloud of all words from Metal and Country 
```{r, echo=FALSE}
library(wordcloud)
par(mfrow=c(1,2))
tidy.Metal <- subset(dt_lyrics, genre == "Metal") %>% unnest_tokens(word, stemmedwords)
count.Metal <- tidy.Metal %>% count(word)
wordcloud(count.Metal$word, count.Metal$n,
          scale=c(3,0.2),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8, "Accent"))

tidy.Coun <- subset(dt_lyrics, genre == "Country") %>% unnest_tokens(word, stemmedwords)
count.Coun <- tidy.Coun %>% count(word)
wordcloud(count.Coun$word, count.Coun$n,
          scale=c(3,0.2),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8, "Accent"))
```


#####By finding "kill", "hate", "dead", "cry" ect strong words from Metal, and "baby", "life", "home" ect temperance words from Country, we can also show the conclusion above. Therefore, Metal is a stronger emotional genre, compared with Country. 














